### 2016-06-08 capability-machine.tex
small mistake in tck disp lemma

 Given $\Phi$, if $\memheap$ contains the ticket dispenser program starting at the address labelled $\init$, $\memreg(\pcreg) = (\rwx,\init,\init+\var{proglen}-1,\init)$, $\memreg(\rio) = (\readwrite,0,1,0)$, and $\Phi \rightarrow^* (\halted,\Phi')$, then the I/O address (that is $\memheap[\Phi'](0)$) contains either $-1$ or a number that is $\geq 0$ and even.

>>>>

 Given $\Phi$, if $\memheap$ contains the ticket dispenser program starting at the address labelled $\init$, $\memreg(\pcreg) = (\rwx,\init,\init+\var{proglen}-1,\init)$, $\memreg(\rio) = (\readwrite,0,0,0)$, and $\Phi \rightarrow^* (\halted,\Phi')$, then the I/O address (that is $\memheap[\Phi'](0)$) contains either $-1$ or a number that is $\geq 0$ and even.
